Sample-Based Determination of Angular Observables

### 2014-06-24 draft.tex
small update

\preprint{SI-HEP-2014-xx}
\title{Sample-Based Determination of Angular Observables}
\author{Frederik Beaujean}
\email{frederik.beaujean@lmu.de}
\affiliation{C2PAP, Universe Cluster, Ludwig-Maximilians-Universit\"at M\"unchen, Garching, Germany}
\author{Marcin Chrzaszcz}
\email{chrzaszcz.marcin@gmail.com}
\author{Nicola Serra}
\email{nicola.serra@cern.ch}
\affiliation{Physik-Institut, Universit\"at Z\"urich, Z\"urich, Switzerland}
\author{Danny van Dyk}
\email{vandyk@tp1.physik.uni-siegen.de}
\affiliation{Theoretische Physik 1, Naturwissenschaftlich-Technische Fakult\"at,
Universit\"at Siegen, Siegen, Germany}

@@

The determination of the coefficients $\eps_i^{(j)}$ that parametrize the detectory effects is generally
a difficult task. Here, we will show a systematic method to determine these coefficients. \dots

@@

The work of D.v.D has been supported by the Bundesministerium f\"ur Bildung und Forschung (BMBF).
\dots
\danny{Potential people to read the manuscript: Jochen Dingfelder (Belle-II, Bonn), Ulrik Egede (LHCb, Imperial London), Christoph Langenbruch (LHCb, Warwick), Michel De Cian (LHCb, Heidelberg).}
D.v.D would like to thank Gudrun Hiller and Martin Jung for discussing the results of \cite{Das:2014xx} prior to publication.

>>>>

\preprint{SI-HEP-2014-xx}
\title{Sample-Based Determination of Angular Observables}
\author{Frederik Beaujean}
\email{frederik.beaujean@lmu.de}
\affiliation{C2PAP, Universe Cluster, Ludwig-Maximilians-Universit\"at M\"unchen, Garching, Germany}
\author{Marcin Chrzaszcz}
\email{marcin.chrzaszcz@uzh.ch}
\author{Nicola Serra}
\email{nicola.serra@cern.ch}
\affiliation{Physik-Institut, Universit\"at Z\"urich, Z\"urich, Switzerland}
\author{Danny van Dyk}
\email{vandyk@tp1.physik.uni-siegen.de}
\affiliation{Theoretische Physik 1, Naturwissenschaftlich-Technische Fakult\"at,
Universit\"at Siegen, Siegen, Germany}

@@

The determination of the coefficients $\eps_i^{(j)}$ that parametrize the detectory effects is generally
a difficult task. Here, we will show a systematic method to determine these coefficients.\\
One starts from generating a flap phase space MonteCarlo sample. Simulated events are then put thought the detector simulation, and selection requirements. Since flap phase space ensures flat distribution of angles on the generated level, the only non zero moment is one associated to Fl. Measuring the moments of this MC sample leads will etc. Mayby this should be an appendix.

@@

The work of D.v.D has been supported by the Bundesministerium f\"ur Bildung und Forschung (BMBF).
\dots
\danny{Potential people to read the manuscript: Jochen Dingfelder (Belle-II, Bonn), Ulrik Egede (LHCb, Imperial London), Christoph Langenbruch (LHCb, Warwick), Michel De Cian (LHCb, Heidelberg), Adrian Bevan (ATLAS, Queen Mary)  }
D.v.D would like to thank Gudrun Hiller and Martin Jung for discussing the results of \cite{Das:2014xx} prior to publication.
